Many-spin entanglement in multiple quantum NMR with a dipolar ordered initial state

### 2020-05-17 manuscript.tex
Fix figure: low bound of FI

\begin{figure}
  	\includegraphics[width=0.95\linewidth]{fisher_low_bound_n101.eps}
	\caption{
	    The dependence of the lower bound on the quantum Fisher Information $F_\mathrm{Q} = 2 M_{2}$ 
	    on the dimensionless time $D\tau$ at $N=101$.
	    a) $T=6\cdot10^{-4}$~K, the inequality~(\ref{eq:20}) yields the region of pair entanglement (k+1=2), the region is above the horizontal line; 
	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=32$~and~$k=46$; 
	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=47$ and k=$86$) bound the strip with many-spin entanglement;
	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $47-92$ spins emerge.
	}
	\label{fig:2}
\end{figure}

@@

The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
One can see from Fig.~(\ref{fig:2}a) that only pair entanglement exists at the temperature $T=6\cdot10^{-4}$~K.
At the temperature $T=3.2\cdot10^{-4}$, one can see a strip in Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
Thus, there is many-spin entanglement in spin clusters consisting of 33-47 spins at the temperature $3.2\cdot10^{-4}$~K.
When the temperature decreases, the width of the strip, in which many-spin entanglement exists, increases. 
At the temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)), clusters of 48-87 entangled spins emerge, and at the temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)), we have 47-92 entangled spins.

>>>>

\begin{figure}
  	\includegraphics[width=0.95\linewidth]{fisher_low_bound_n101.eps}
	\caption{
	    The dependence of the lower bound on the quantum Fisher Information $F_\mathrm{Q} = 2 M_{2}$ 
	    on the dimensionless time $D\tau$ at $N=101$.
	    a) $T=6\cdot10^{-4}$~K, the inequality~(\ref{eq:20}) yields the region of pair entanglement (k+1=2), the region is above the horizontal line; 
	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=19$~and~$k=46$; 
	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=18$ and k=$86$) bound the strip with many-spin entanglement;
	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $10-92$ spins emerge.
	}
	\label{fig:2}
\end{figure}

@@

The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
One can see from Fig.~(\ref{fig:2}a) that only pair entanglement exists at the temperature $T=6\cdot10^{-4}$~K.
At the temperature $T=3.2\cdot10^{-4}$, one can see a strip in Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when $19 \leq k \leq 46$.
Thus, there is many-spin entanglement in spin clusters consisting of 20-47 spins at the temperature $3.2\cdot10^{-4}$~K.
When the temperature decreases, the width of the strip, in which many-spin entanglement exists, increases. 
At the temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)), clusters of 19-87 entangled spins emerge, and at the temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)), we have 11-92 entangled spins.
